---
title: "all_analyses"
author: "Hilary Killam"
date: "2023-06-14"
output: html_document
---
# Setup
## Load packages
```{r setup, include=FALSE}

# we had several compabatibility issues when trying to load packages using groundhog. 
# we decided to inform the users about our R and packages versions below. 
# however, if you want to give it a try on groundhog, just set the following variable to TRUE 
groundhog_load <- FALSE

if(groundhog_load == TRUE){source("groundhog_library.R")} else{
  
# R version 4.1.2 (2021-11-01)

## 1. Load packages - version 
library(weights) # 1.0.4 
library(eyetrackingR) # 0.2.0
library(tidyverse) # 1.3.1
library(lme4) # 1.1-28 
library(lmerTest) # 3.1-3
library(broom) # 0.7.10
library(corrr) # 0.4.3 
library(ez) # 4.4-0
library(ggpubr) # 0.4.0
library(tidylog) # 1.0.2 
library(janitor) # 2.1.0
library(here) # 1.0.1 
library(patchwork) # 1.1.1
library(car) # 3.0-12
library(metafor) # 3.0-2
library(effectsize) # 0.6.0.1
library(pwr) # 1.3-0
library(simr) # 1.0.6
library(TOSTER) # 0.6.0
library(parameters) # 0.20.2
library(sjPlot) # 2.8.12
library(sjstats) # 0.18.2 
library(see) # 0.7.4

}

# limit sceintifc notation
options(scipen = 999)

# useful function
`%notin%` <- negate(`%in%`)

```

## Load data
```{r load_data}

#-------------------------------------------------Eyetracking data

load(here("data/2023-05-16_data_ready_for_analysis.Rda"))
#write.csv(dataset, file = "data_ready_for_analysis.csv") # generates a 1.6GB file

#-------------------------------------------------Participant data

participants <- read_csv(here("data", "2021-11-04_participant_data_for_upload.csv")) %>% 
  filter(!is.na(baby_id))#288 total 

#-------------------------------------------------Subset of participants from the Da Estrela paper

da_estrela_keepers <- read_csv(here("data", "da_estrela_original_keepers.csv"))

#-------------------------------------------------Vocabulary data

vocab_raw <- read.csv(here("data/vocabulary_data.csv"))
vocab <- vocab_raw %>% 
  select(recording_name, cdi_comp_eng, cdi_comp_fr, total_vocab_comp) %>% 
  drop_na(recording_name) %>% 
  rename(id = recording_name)

```

## Clean data
```{r clean_data}

#-------------------------------------------------Prep eyetracking data

dataset <- dataset %>%
  #remove some trials for technical lagging (When we plotted the data, these trials took longer than they should have and so TOBII lagged. Remove them)
   mutate(exclude = case_when(id == "Novel_14_S124" & trial_number == 6 ~ TRUE, 
                             id == "Novel_14_S89" & trial_number == 4 ~ TRUE,
                             id == "Novel_14_S136" & trial_number == 17 ~ TRUE,
                             id == "NovelDom_14_S09" & trial_number == 20 ~ TRUE,
                             id == "NovelDom14_S26_43142" & trial_number == 18 ~ TRUE,
                             TRUE ~ FALSE)) %>% 
  filter(exclude != TRUE) %>%
  
  #Recode trial_lang variable as "familiarity"
  mutate(trial_lang = case_when(trial_lang == "best" ~ "most_familiar",
                                trial_lang == "non-best" ~ "least_familiar")) %>%
  rename(familiarity = trial_lang) %>%
  
  #create zeroed time stamp for trials and condition variables
  group_by(id, recording_number, trial_number) %>%
  mutate(trial_from_zero = recording_timestamp - min(recording_timestamp),
         group = case_when(str_detect(lang_group, "bilingual") ~ "Bilinguals",
                           str_detect(lang_group, "monolingual") ~ "Monolinguals"),
         stimulus_set = as.factor(stimulus_set),
         condition_language = case_when(str_detect(study_order, "E") ~ "english",
                                        str_detect(study_order, "F") ~ "french",
                                        TRUE ~ "bilingual"),
         condition = case_when(condition_language == dom_lang ~ "single_lang_native",
                               condition_language == "bilingual" ~ "dual_lang",
                               TRUE ~ "single_lang_foreign"),
         trad_analysis_group = paste0(lang_group, "_", condition),
         experiment = case_when(trad_analysis_group == "bilingual_freng_dual_lang" ~ "experiment_1",
                                trad_analysis_group == "bilingual_other_dom_dual_lang" ~ "experiment_2",
                                trad_analysis_group == "bilingual_other_nondom_dual_lang" ~ "experiment_3",
                                trad_analysis_group == "monolingual_dual_lang" ~ "experiment_4",
                                trad_analysis_group == "bilingual_freng_single_lang_native" ~ "experiment_5",
                                trad_analysis_group == "monolingual_single_lang_native" ~ "experiment_6",
                                trad_analysis_group == "monolingual_single_lang_foreign" ~ "experiment_7"),
         stimulus_to_baby = case_when(carrier_language == dom_lang ~ "dominant",
                                      carrier_language != dom_lang & lang_group == "monolingual" ~ "foreign",
                                      dom_lang == "other" & best_lang == carrier_language ~ "nondominant",
                                      dom_lang == "other" & best_lang != carrier_language ~ "foreign",
                                      lang_group == "bilingual_freng" & carrier_language != dom_lang ~ "nondominant",
                                      lang_group == "bilingual_other_dom" & carrier_language != dom_lang ~ "foreign",
                                      TRUE ~ "other")) %>%
  group_by(study_order) %>%
  mutate(first_word_presented_training = case_when(trial_number == 1 ~ target_word,
                                                   TRUE ~ NA_character_)) %>%
  fill(first_word_presented_training) %>%
  ungroup()

#Make sure no NAs for condition
dataset %>% count(condition)
#Make sure correct number of groups (7 plus 3 that will get filtered out)
dataset %>% count(experiment, trad_analysis_group)

```

## Split data
```{r split_data}

#-------------------------------------------------Split dataset for analyses

#-----------------Traditional

#Filter to keepers for the traditional analysis (remove excluded)
data_trad <- dataset %>%
  filter(keeper_traditional == 1)

#Split into Training and Test
data_trad_test <- data_trad %>%
  filter(trial_type == 'test')

data_trad_training <- data_trad %>%
  filter(trial_type == 'training')


#-----------------Updated

#Filter to keepers for the updated analysis (remove excluded and trilinguals) and merge vocab data
data_updated <- dataset %>%
  filter(keeper_new_analysis == 1) %>%
  filter(lang_group != "trilingual") %>% 
  left_join(., vocab, by = "id")

#Split into Training and Test
data_updated_test <- data_updated %>%
  filter(trial_type == 'test')

data_updated_training <- data_updated %>%
  filter(trial_type == 'training')

```

## Prep data
### Make eyetracking datasets
#### Traditional
```{r prep_data_trad}

#-------------------------------------------------Traditional
#-----------------Prep Trad Training data

data_trad_training <- make_eyetrackingr_data(data_trad_training,
                               participant_column = "id",
                               trial_column = "trial_number",
                               time_column = "trial_from_zero",
                               trackloss_column = "trackloss",
                               aoi_columns = c('training_AOI', 'training_away_AOI'),
                               treat_non_aoi_looks_as_missing = FALSE) #false because these AOIs are not the same size

#-----------------Prep Trad Test data

data_trad_test <- make_eyetrackingr_data(data_trad_test,
                               participant_column = "id",
                               trial_column = "trial_number",
                               time_column = "trial_from_zero",
                               trackloss_column = "trackloss",
                               aoi_columns = c('target_AOI', 'distractor_AOI'),
                               treat_non_aoi_looks_as_missing = TRUE)

#-----------------Subset Trad dataset to Training window

response_window_trad_training <- subset_by_window(data_trad_training, 
                                    window_start_time = 1700, #200ms after onset of initial carrier phrase, which lasts 1500 ms
                                    window_end_time = 11000, #End of trial. Approx. 11 seconds
                                    rezero = FALSE)

#-----------------Subset Trad dataset to Test window

response_window_trad_test <- subset_by_window(data_trad_test, 
                                    window_start_time = 3200, #3200ms after noun onset
                                    window_end_time = 10000, #End of trial. Approx. 10 seconds
                                    rezero = FALSE)

#-----------------Subset Trad dataset to Test window before any utterance

prename_pref_window_trad_test <- subset_by_window(data_trad_test, 
                                    window_start_time = 0, #beginning of trial
                                    window_end_time = 3000, #first word onset
                                    rezero = FALSE)

```

#### Updated
```{r prep_data_updated}

#-------------------------------------------------Updated
#-----------------Prep Updated Training data

data_updated_training <- make_eyetrackingr_data(data_updated_training,
                               participant_column = "id",
                               trial_column = "trial_number",
                               time_column = "trial_from_zero",
                               trackloss_column = "trackloss",
                               aoi_columns = c('training_AOI', 'training_away_AOI'),
                               treat_non_aoi_looks_as_missing = FALSE) #false because these AOIs are not the same size

#-----------------Prep Updated Test data

data_updated_test <- make_eyetrackingr_data(data_updated_test,
                               participant_column = "id",
                               trial_column = "trial_number",
                               time_column = "trial_from_zero",
                               trackloss_column = "trackloss",
                               aoi_columns = c('target_AOI', 'distractor_AOI'),
                               treat_non_aoi_looks_as_missing = TRUE)

#-----------------Subset Updated dataset to Training window

response_window_updated_training <- subset_by_window(data_updated_training, 
                                    window_start_time = 3700, #3700ms after noun onset
                                    window_end_time = 11000, #End of trial. Approx. 11 seconds
                                    rezero = FALSE)

#-----------------Subset Updated dataset to Test window

response_window_updated_test <- subset_by_window(data_updated_test, 
                                    window_start_time = 3200, #3200ms after noun onset
                                    window_end_time = 10000, #End of trial. Approx. 10 seconds
                                    rezero = FALSE)

#-----------------Subset Updated dataset to Test window before any utterance

prename_pref_window_updated_test <- subset_by_window(data_updated_test, 
                                    window_start_time = 0, #beginning of trial
                                    window_end_time = 3000, #first word onset
                                    rezero = FALSE)

```

### Trackloss

#### Traditional
```{r trackloss_trad}

#-------------------------------------------------Traditional

n_pre_trackloss_trad <- n_distinct(response_window_trad_test$id)

trackloss_trad_test <- trackloss_analysis(response_window_trad_test)

response_window_trad_test <- clean_by_trackloss(data = response_window_trad_test,
                                   trial_prop_thresh = (1 - 750/(10000 - 3200))) # Need at least 750ms looking = 750/(10000 - 3200) divide by trial length

#------------------Keep only kids who have at least 1 test trial per target word for Traditional analysis
data_trad_test <- response_window_trad_test %>%
  group_by(id) %>%
  mutate(num_words = n_distinct(target_word)) %>% 
  filter(num_words == 2)

```

#### Updated
```{r trackloss_updated}

#-------------------------------------------------Updated

#------------------Test

n_pre_trackloss_updated <- n_distinct(response_window_updated_test$id)

trackloss_updated_test <- trackloss_analysis(response_window_updated_test)

data_updated_test <- clean_by_trackloss(data = response_window_updated_test,
                                   trial_prop_thresh = (1 - 750/(10000 - 3200))) # Need at least 750ms looking = 750/(10000 - 3200) divide by trial length

```

### Final sample

#### Traditional
```{r final_sample_trad}

#-------------------------------------------------Traditional

#-----------------------Get final sample IDs
final_sample_ids_trad <- data_trad_test %>% 
  select(id, experiment, condition) %>% 
  distinct() %>% 
  mutate(id = as.character(id)) %>% 
  ungroup() 

final_sample_trad <- final_sample_ids_trad %>%
  left_join(participants, by = c("id" = "recording_name"))
```

#### Updated
```{r final_sample_updated}

#-------------------------------------------------Updated

#-----------------------Get final sample IDs
final_sample_ids_updated <- data_updated_test %>% 
  select(id, experiment, condition) %>% 
  distinct() %>% 
  mutate(id = as.character(id)) %>% 
  ungroup() 

final_sample_updated <- final_sample_ids_updated %>%
  left_join(participants, by = c("id" = "recording_name"))

```
### Make T-test datasets
#### Traditional only
```{r ttest_data}

#-------------------------------------------------t-tests data
#------------------t-test data, all conditions

data_ttest_trad_test <- describe_data(data_trad_test, 
                describe_column = "target_AOI", 
                group_columns = c("id", "lang_group", "familiarity", "trial_type", "target_word", "best_lang", "per_carrier_lang", "condition", "stimulus_to_baby", "trad_analysis_group", "first_word_presented_training", "experiment")) %>%
  mutate(total_ms = (1000/60)*N) %>%
  mutate(looking_ms = total_ms * Mean) %>%
  arrange(lang_group)

#------------------Proportion looking by trial

data_prop_by_trial_trad_test <- make_time_window_data(data_trad_test, 
                                                    aois = "target_AOI",
                                                    predictor_columns=c("lang_group", "familiarity", "trial_type", "trial_number_of_type", "per_carrier_lang", "condition", "trad_analysis_group", "target_word", "stimulus_to_baby", "first_word_presented_training"),
                                                    summarize_by = c("id", "trial_number"),
                                                    other_dv_columns = c("pupil_left", "pupil_right")) 

#------------------Proportion looking by word
data_prop_by_word_trad_test <- make_time_window_data(data_trad_test, 
                                                    aois = "target_AOI",
                                                    predictor_columns = c("lang_group", "familiarity", "trial_type", "trial_number_of_type", "per_carrier_lang", "condition", "trad_analysis_group", "target_word", "stimulus_to_baby", "first_word_presented_training", "experiment"),
                                                    summarize_by = "id",
                                                    other_dv_columns = c("pupil_left", "pupil_right")) %>%
   #this next step takes the by trial proportions and averages them for kids with more than one trial per word. This produces a different Prop value than when it's produced by dividing all the samples in AOI by all the samples total.
  group_by(id, lang_group, familiarity, trial_type, target_word, stimulus_to_baby, trad_analysis_group, condition, experiment) %>%
  summarize(Prop = mean(Prop))

```

### Make prenaming preference data

#### Traditional
```{r prename_trad}
#-------------------------------------------------Prenaming preference by object
#do participants look more to one object over the other, before the object names are spoken?

prename_data_trad_test <- prename_pref_window_trad_test %>%
  #restrict to our final sample
  filter(id %in% final_sample_ids_trad$id) %>%
  mutate(looking_at_kem = case_when(target_word == "kem" & target_AOI == TRUE ~ 1,
                                    target_word == "bos" & distractor_AOI == TRUE ~ 1,
                                    target_word == "kem" & distractor_AOI == TRUE ~ 0,
                                    target_word == "bos" & target_AOI == TRUE ~ 0),
         looking_at_bos = case_when(target_word == "bos" & target_AOI == TRUE ~ 1,
                                    target_word == "kem" & distractor_AOI == TRUE ~ 1,
                                    target_word == "bos" & distractor_AOI == TRUE ~ 0,
                                    target_word == "kem" & target_AOI == TRUE ~ 0)) %>% 
  group_by(id, lang_group, condition, experiment) %>%
  summarize(pref_kem = mean(looking_at_kem == TRUE, na.rm = TRUE),
         pref_bos = mean(looking_at_bos == TRUE, na.rm = TRUE)) %>%
  pivot_longer(c("pref_kem", "pref_bos"), names_to = c("object"), values_to = "prop") %>%
  mutate(object = str_remove(object, "pref_")) %>%
  ungroup() 

#-----------------------Save IDs and baseline preference by participant and word
baseline_preference_trad <- prename_data_trad_test %>%
  select(id, object, prop) %>%
  pivot_wider(names_from = "object", values_from = "prop") %>%
  rename(preference_kem = kem, 
         preference_bos = bos)

```

#### Updated
```{r prename_updated}
#-------------------------------------------------Prenaming preference by object

prename_data_updated_test <- prename_pref_window_updated_test %>%
  #restrict to our final sample
  filter(id %in% final_sample_ids_updated$id) %>%
  mutate(looking_at_kem = case_when(target_word == "kem" & target_AOI == TRUE ~ 1,
                                    target_word == "bos" & distractor_AOI == TRUE ~ 1,
                                    target_word == "kem" & distractor_AOI == TRUE ~ 0,
                                    target_word == "bos" & target_AOI == TRUE ~ 0),
         looking_at_bos = case_when(target_word == "bos" & target_AOI == TRUE ~ 1,
                                    target_word == "kem" & distractor_AOI == TRUE ~ 1,
                                    target_word == "bos" & distractor_AOI == TRUE ~ 0,
                                    target_word == "kem" & target_AOI == TRUE ~ 0)) %>% 
  group_by(id, lang_group, condition, experiment) %>%
  summarize(pref_kem = mean(looking_at_kem == TRUE, na.rm = TRUE),
         pref_bos = mean(looking_at_bos == TRUE, na.rm = TRUE)) %>%
  pivot_longer(c("pref_kem", "pref_bos"), names_to = c("object"), values_to = "prop") %>%
  mutate(object = str_remove(object, "pref_")) %>%
  ungroup() 

#-----------------------Save IDs and baseline preference by participant and word
baseline_preference_updated <- prename_data_updated_test %>%
  select(id, object, prop) %>%
  pivot_wider(names_from = "object", values_from = "prop") %>%
  rename(preference_kem = kem, 
         preference_bos = bos)

```

### Make lmer datasets
#### Updated only

```{r data_updated}

#-------------------------------------------------Training
# summary of total looking time during training for each participant on each trial
data_lmer_updated_training_by_trial <- 
  data_updated_training %>% 
  filter(trackloss == FALSE) %>% #valid rows only
  make_time_window_data(data = ., 
                        aois = "training_AOI",
                        predictor_columns = c("lang_group", "carrier_language", 
                                              "best_lang",
                                              "target_word"),
                        summarize_by = "id") %>% 
  mutate(looking_time = SamplesInAOI * (1000/60)) # assuming 60Hz

## summary by participant averaged across trials
data_lmer_updated_training_by_participant <- 
  data_lmer_updated_training_by_trial %>% 
  group_by(id) %>% 
  summarise(total_looking_time_training = sum(looking_time, na.rm = T)) 

#-------------------------------------------------Test

## join with training df
data_updated_test <-
  data_updated_test %>% 
  left_join(., data_lmer_updated_training_by_participant, by = "id")

# aggregate for each participant on each trial
data_lmer_updated_test_by_trial <- 
  data_updated_test %>% 
  make_time_window_data(data = .,
                        aois = "target_AOI",
                        predictor_columns = c("lang_group", "familiarity", "trial_type", "best_lang", "per_carrier_lang",
                                              "condition", "target_word", "stimulus_to_baby",
                                              "per_fr", "per_eng", 
                                              "cdi_comp_eng", "cdi_comp_fr", "total_vocab_comp",
                                              "total_looking_time_training"),   
                        other_dv_columns = c("pupil_left", "pupil_right")) %>% 

  mutate(per_exposure_target = case_when(familiarity == "most_familiar" & best_lang == "french" ~ per_fr,
                                         familiarity == "most_familiar" & best_lang == "english" ~ per_eng,
                                         familiarity == "least_familiar" & best_lang == "french" ~ per_eng,
                                         familiarity == "least_familiar" & best_lang == "english" ~ per_fr,
                                         TRUE ~ 0),
         per_exposure_other = case_when(familiarity == "most_familiar" & best_lang == "french" ~ per_eng,
                                        familiarity == "most_familiar" & best_lang == "english" ~ per_fr,
                                        familiarity == "least_familiar" & best_lang == "french" ~ per_fr,
                                        familiarity == "least_familiar" & best_lang == "english" ~ per_eng,
                                        TRUE ~ 0),
         vocab_target = case_when(familiarity == "most_familiar" & best_lang == "french" ~ cdi_comp_fr,
                                  familiarity == "most_familiar" & best_lang == "english" ~ cdi_comp_eng,
                                  familiarity == "least_familiar" & best_lang == "french" ~ cdi_comp_eng,
                                  familiarity == "least_familiar" & best_lang == "english" ~ cdi_comp_fr,
                                  TRUE ~ as.integer(0)),
         vocab_target = case_when(is.na(vocab_target) ~ as.integer(0),
                                  TRUE ~ vocab_target)
         ) %>% 
  mutate(familiarity = as_factor(familiarity)) %>%
  left_join(baseline_preference_updated, by = "id") %>%
  mutate(difference_score = case_when(target_word == "kem" ~ Prop - preference_kem,
                                      target_word == "bos" ~ Prop - preference_bos))

# final sample
data_lmer_updated_test_by_trial %>% 
  distinct(id) %>% 
  count() # 148 participants

# distribution of proportion of looking
hist(data_lmer_updated_test_by_trial$Prop)

```

# Descriptives
## Traditional
```{r descriptives_n}

#-------------------------------------------------Sample size

print(paste("Final sample size for traditional analysis:", n_distinct(final_sample_trad$id)))

#-------------------------------------------------Excluded due to trackloss

print(paste("Excluded due to trackloss for traditional analysis:", 
            n_pre_trackloss_trad - n_distinct(response_window_trad_test$id)))

#-------------------------------------------------Excluded due to not having data for both words (Trad only)

print(paste("Number of participants excluded because they don't have data for both words in test trials:", n_distinct(response_window_trad_test$id) - n_distinct(final_sample_trad$id)))

#-----------------------Age, sex by lang group

final_sample_trad %>%
  ungroup() %>%
  select(id, gender_written, total_age_days_excel, lang_group, experiment) %>%
  distinct() %>%
  mutate(lang_group = case_when(str_detect(lang_group, "other") ~"bilingual_other",
                                TRUE ~ lang_group)) %>%
  group_by(lang_group) %>%
  summarize(count = length(unique(id)),
            avg_age_days = floor(mean(total_age_days_excel, na.rm = TRUE)),
            sd_age_days = (sd(total_age_days_excel, na.rm = TRUE)),
            min_age_days = min(total_age_days_excel),
            max_age_days = max(total_age_days_excel),
            avg_age = avg_age_days/30.436875, #divide by average days in a month
            avg_months = floor(avg_age),
            avg_days = floor((avg_age - avg_months) * 30.436875),
            min_age = min_age_days/30.436875,
            min_months = floor(min_age),
            min_days = floor((min_age - min_months) * 30.436875),
            max_age = max_age_days/30.436875,
            max_months = floor(max_age),
            max_days = floor((max_age - max_months) * 30.436875),            
            num_female = sum(gender_written == "female")) %>%
  select(-avg_age_days, -min_age_days, -max_age_days, -avg_age, -min_age, -max_age)

#-----------------------Age, sex for overall sample

final_sample_trad %>%
  ungroup() %>%
  select(id, gender_written, total_age_days_excel, lang_group, experiment) %>%
  distinct() %>%
  summarize(count = length(unique(id)),
            avg_age_days = floor(mean(total_age_days_excel, na.rm = TRUE)),
            sd_age_days = (sd(total_age_days_excel, na.rm = TRUE)),
            min_age_days = min(total_age_days_excel),
            max_age_days = max(total_age_days_excel),
            avg_age = avg_age_days/30.436875, #divide by average days in a month
            avg_months = floor(avg_age),
            avg_days = floor((avg_age - avg_months) * 30.436875),
            min_age = min_age_days/30.436875,
            min_months = floor(min_age),
            min_days = floor((min_age - min_months) * 30.436875),
            max_age = max_age_days/30.436875,
            max_months = floor(max_age),
            max_days = floor((max_age - max_months) * 30.436875),            
            num_female = sum(gender_written == "female")) %>%
  select(-avg_age_days, -min_age_days, -max_age_days, -avg_age, -min_age, -max_age)

#------------------Exposure to langauges

final_sample_trad %>%
  ungroup() %>%
  select(id, lang_group, dom_lang, best_lang, per_eng, per_fr, per_other) %>%
  distinct() %>%
  group_by(lang_group, dom_lang) %>%
  summarize(per_en = mean(per_eng, na.rm = TRUE),
            num = length(unique(id)),
            per_fr = mean(per_fr, na.rm = TRUE),
            per_other = mean(per_other, na.rm = TRUE)) %>%
  mutate(per_en_and_fr = per_en + per_fr)

#------------------Means by experiment
data_ttest_trad_test %>%
  group_by(trad_analysis_group, familiarity, stimulus_to_baby, condition, experiment) %>%
  summarise(target.mean = mean(Mean), 
            target.sd = sd(Mean), 
            n = length(unique(id)))

#------------------means by word for single-lang condition
data_ttest_trad_test %>%
  filter(str_detect(condition, "single_lang")) %>%
  group_by(trad_analysis_group, familiarity, stimulus_to_baby, condition, target_word, experiment) %>%
  summarise(target.mean = mean(Mean), target.sd = sd(Mean), n = length(unique(id)))

#------------------N participants per language group
data_ttest_trad_test %>% 
  ungroup() %>% 
  distinct(id, trad_analysis_group, condition, experiment) %>% 
  count(trad_analysis_group, condition, experiment)

```

## Updated
```{r descriptives_age}

#-------------------------------------------------Sample size

print(paste("Final sample size for updated analysis:", n_distinct(final_sample_updated$id))) 

#-------------------------------------------------Excluded due to trackloss

print(paste("Excluded due to trackloss for updated analysis:", 
            n_pre_trackloss_updated - n_distinct(data_updated_test$id)))

#-------------------------------------------------Difference between Trad and Updated sample 

only_1_trial_in_trad <- response_window_trad_test %>% 
  anti_join(data_trad_test, by = "id") %>% 
  distinct(id) %>% 
  mutate(only_1_trial_in_trad = "yes")

infants_added <- final_sample_updated %>% 
  mutate(added = ifelse(is.na(reason_exclusion), 0, 1)) %>%
  left_join(only_1_trial_in_trad, by = "id") %>%
  mutate(added = case_when(only_1_trial_in_trad == "yes" ~ 1,
                           TRUE ~ added),
         added = case_when(is.na(added) ~ 0,
                           TRUE ~ added)) %>% 
  filter(added == 1)

#-----------------------Age, sex for added infants

infants_added %>%
  ungroup() %>%
  select(id, gender_written, total_age_days_excel) %>%
  distinct() %>%
  summarize(count = length(unique(id)),
            avg_age_days = floor(mean(total_age_days_excel, na.rm = TRUE)),
            sd_age_days = (sd(total_age_days_excel, na.rm = TRUE)),
            min_age_days = min(total_age_days_excel),
            max_age_days = max(total_age_days_excel),
            avg_age = avg_age_days/30.436875, #divide by average days in a month
            avg_months = floor(avg_age),
            avg_days = floor((avg_age - avg_months) * 30.436875),
            min_age = min_age_days/30.436875,
            min_months = floor(min_age),
            min_days = floor((min_age - min_months) * 30.436875),
            max_age = max_age_days/30.436875,
            max_months = floor(max_age),
            max_days = floor((max_age - max_months) * 30.436875),            
            num_female = sum(gender_written == "female")) %>%
  select(-avg_age_days, -min_age_days, -max_age_days, -avg_age, -min_age, -max_age)

#-----------------------Age, sex for total updated sample

final_sample_updated %>%
  ungroup() %>%
  select(id, gender_written, total_age_days_excel, lang_group) %>%
  distinct() %>%
  summarize(count = length(unique(id)),
            avg_age_days = floor(mean(total_age_days_excel, na.rm = TRUE)),
            sd_age_days = (sd(total_age_days_excel, na.rm = TRUE)),
            min_age_days = min(total_age_days_excel),
            max_age_days = max(total_age_days_excel),
            avg_age = avg_age_days/30.436875, #divide by average days in a month
            avg_months = floor(avg_age),
            avg_days = floor((avg_age - avg_months) * 30.436875),
            min_age = min_age_days/30.436875,
            min_months = floor(min_age),
            min_days = floor((min_age - min_months) * 30.436875),
            max_age = max_age_days/30.436875,
            max_months = floor(max_age),
            max_days = floor((max_age - max_months) * 30.436875),            
            num_female = sum(gender_written == "female")) %>%
  select(-avg_age_days, -min_age_days, -max_age_days, -avg_age, -min_age, -max_age)

#-----------------------average exposure to each language per experimental group for added infants

infants_added %>%
  ungroup() %>%
  select(id, dom_lang, best_lang, per_eng, per_fr, per_other) %>%
  distinct() %>%
  group_by(dom_lang) %>%
  summarize(per_en = mean(per_eng, na.rm = TRUE),
            num = length(unique(id)),
            per_fr = mean(per_fr, na.rm = TRUE),
            per_other = mean(per_other, na.rm = TRUE)) %>%
  mutate(per_en_and_fr = per_en + per_fr)

#-----------------------Most familiar languages for added infants
infants_added %>% 
  distinct(id, dom_lang, best_lang) %>% 
  count(dom_lang, best_lang)

#-----------------------total number of participants by gender per experimental group
final_sample_updated %>%
  group_by(gender_written) %>%
  summarize(n = length(unique(id))) %>%
  filter(gender_written == "female")

#-----------------------How many of our final sample were in Da Estrela's keepers?

final_sample_ids_updated %>% 
  filter(id %in% da_estrela_keepers$id) %>%
  nrow()

```

# Planned analyses

## Traditional

### t-tests against chance
```{r ttests_original}

#-------------------------------------------------Difference in looking time training
#do t-test on dual language condition to see if any difference between looking time depending on stimulus language
response_window_trad_training %>% 
  filter(condition == "dual_lang" & id %in% final_sample_ids_trad$id) %>%
  filter(trackloss == FALSE) %>% # only count valid rows
  group_by(id, target_word, condition, lang_group, trial_number, familiarity, experiment) %>%
  summarize(trial_length = length(id), #num valid rows
            looking_at_target = sum(training_AOI == TRUE, na.rm = TRUE),
            mean_looking_at_target = mean(training_AOI == TRUE, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(trial_length_ms = trial_length * (1000/60),
         looking_time_ms = looking_at_target * (1000/60)) %>%
  group_by(id, lang_group, condition, familiarity, experiment) %>%
  summarize(trial_time = sum(trial_length_ms),
            looking_time = sum(looking_time_ms))%>%
  group_by(lang_group) %>%
  do(broom::tidy(t.test(.$looking_time ~ .$familiarity, data = ., paired = TRUE))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1))

#-------------------------------------------------Dual lang condition against 50% chance
data_ttest_trad_test %>%
  filter(condition == "dual_lang") %>% 
  group_by(trad_analysis_group, familiarity, condition, experiment) %>%
  do(broom::tidy(t.test(.$Mean, mu = .5, data = .))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1)) 

#-------------------------------------------------Single lang condition against 50% chance 
data_ttest_trad_test %>%
  filter(condition != "dual_lang") %>% 
  group_by(trad_analysis_group, condition, familiarity, experiment) %>%
  do(broom::tidy(t.test(.$Mean , mu = .5, data = .))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1)) 

#-------------------------------------------------Data pooled against 50% chance (overall slightly above chance)
data_ttest_trad_test %>%
  do(broom::tidy(t.test(.$Mean, mu = .5, data = .))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1)) 

#-------------------------------------------------Split by target word, only kem is above chance 
data_ttest_trad_test %>%
  group_by(target_word) %>%
  do(broom::tidy(t.test(.$Mean, mu = .5, data = .))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1)) 

#-------------------------------------------------Split by familiarity, only least familiar is above chance
data_ttest_trad_test %>%
  group_by(familiarity) %>%
  do(broom::tidy(t.test(.$Mean, mu = .5, data = .))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1)) 

#-------------------------------------------------Split by familiarity and target word, only kem is above chance
data_ttest_trad_test %>%
  group_by(familiarity, target_word) %>%
  do(broom::tidy(t.test(.$Mean, mu = .5, data = .))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1)) 

#-------------------------------------------------Looking to kem and bos are significantly different from each other
data_ttest_trad_test %>%
  select(id, target_word, Mean) %>%
  pivot_wider(names_from = "target_word", values_from = "Mean") %>%
  do(broom::tidy(t.test(.$kem, .$bos, paired = TRUE, data = .))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1)) 


```

#### Group means
```{r ttests_original_means}

#-------------------------------------------------Group means

#-----------------------Difference in looking time training
response_window_trad_training %>%
  filter(trackloss == FALSE) %>% #only look at valid rows
  filter(condition == "dual_lang" & id %in% final_sample_ids_trad$id) %>%
  group_by(id, target_word, condition, lang_group, trial_number, familiarity, experiment) %>%
  summarize(trial_length = length(id),
            looking_at_target = sum(training_AOI == TRUE, na.rm = TRUE),
            mean_looking_at_target = mean(training_AOI == TRUE, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(trial_length_ms = trial_length * (1000/60),
         looking_time_ms = looking_at_target * (1000/60)) %>%
  group_by(id, lang_group, condition, familiarity, experiment) %>%
  summarize(trial_time = sum(trial_length_ms),
            looking_time = sum(looking_time_ms)) %>%
  group_by(lang_group, condition, familiarity, experiment) %>%
  summarize(trial_time_s = mean(trial_time, na.rm = TRUE)/1000,
            sd_trial_time_s = sd(trial_time, na.rm = TRUE)/1000,
            looking_time_s = mean(looking_time, na.rm = TRUE)/1000,
            sd_looking_time_s = sd(looking_time, na.rm = TRUE)/1000)

#-----------------------Target word means
data_ttest_trad_test %>%
  group_by(target_word) %>%
  summarize(mean = mean(Mean),
            n =n(),
            sd = sd(Mean))

#-----------------------Target word by lang group means
data_ttest_trad_test %>%
  group_by(target_word, lang_group) %>%
  summarize(mean = mean(Mean),
            n =n())

#-----------------------Target word by familiarity means
data_ttest_trad_test %>%
  group_by(target_word, familiarity) %>%
  summarize(mean = mean(Mean),
            n =n())

#-----------------------Target word, familiarity, condition means
data_ttest_trad_test %>%
  group_by(target_word, familiarity, condition) %>%
  summarize(mean = mean(Mean),
            n =n()) %>%
  arrange(desc(n))


#-----------------------Experiment, target_word, familiarity, condition means
data_ttest_trad_test %>%
  group_by(experiment, target_word, familiarity, condition) %>%
  summarize(mean = mean(Mean),
            n =n()) %>%
  arrange(desc(n))

```

### t-tests preference corrected
```{r ttests_corrected}

#-----------------------Difference between looking to objects before utterances? Yes, slight kem preference
prename_data_trad_test %>%
  do(broom::tidy(t.test(.$prop ~ .$object, paired = TRUE, alternative = "two.sided"))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1))

#different way to get the same result:
prename_data_trad_test %>%
  filter(object == "kem") %>%
  do(broom::tidy(t.test(.$prop, mu = 0.5, data = .))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1)) 

prename_data_trad_test %>%
  group_by(object) %>%
  summarize(mean_prop = mean(prop),
            sd_prop = sd(prop))

#-------------------------------------------------Dual lang condition, prop looking minus prename preference compared to zero
data_ttest_trad_test %>%
  left_join(baseline_preference_trad, by = "id") %>% 
  mutate(compare_value = case_when(target_word == "kem" ~ Mean - preference_kem,
                                   target_word == "bos" ~ Mean - preference_bos)) %>% 
  filter(condition == "dual_lang") %>% 
  group_by(trad_analysis_group, familiarity, condition, experiment) %>%
  do(broom::tidy(t.test(.$compare_value, mu = 0, data = .))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1)) 

#-------------------------------------------------Single lang condition, prop looking minus prename preference against zero
data_ttest_trad_test %>%
  left_join(baseline_preference_trad, by = "id") %>% 
  mutate(compare_value = case_when(target_word == "kem" ~ Mean - preference_kem,
                                   target_word == "bos" ~ Mean - preference_bos)) %>% 
  filter(condition != "dual_lang") %>% 
  group_by(trad_analysis_group, condition, familiarity, experiment, target_word) %>%
  do(broom::tidy(t.test(.$compare_value , mu = 0, data = .))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1)) 

#-------------------------------------------------Data pooled, prop looking minus prename preference against zero (overall, pooled, yes kids are learning, DV is slightly above zero)
data_ttest_trad_test %>%
  left_join(baseline_preference_trad, by = "id") %>% 
  mutate(compare_value = case_when(target_word == "kem" ~ Mean - preference_kem,
                                   target_word == "bos" ~ Mean - preference_bos)) %>%
  do(broom::tidy(t.test(.$compare_value, mu = 0, data = .))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1)) 

#-------------------------------------------------Split by target word, prop looking minus prename preference against zero ()
data_ttest_trad_test %>%
  left_join(baseline_preference_trad, by = "id") %>% 
  mutate(compare_value = case_when(target_word == "kem" ~ Mean - preference_kem,
                                   target_word == "bos" ~ Mean - preference_bos)) %>% 
  group_by(target_word) %>%
  do(broom::tidy(t.test(.$compare_value, mu = 0, data = .))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1)) 

#-------------------------------------------------Split by familiarity, prop looking minus prename preference against zero
data_ttest_trad_test %>%
  left_join(baseline_preference_trad, by = "id") %>% 
  mutate(compare_value = case_when(target_word == "kem" ~ Mean - preference_kem,
                                   target_word == "bos" ~ Mean - preference_bos)) %>%
  group_by(familiarity) %>%
  do(broom::tidy(t.test(.$compare_value, mu = 0, data = .))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1)) 

#-------------------------------------------------Split by familiarity and target word, prop looking minus prename preference against zero
data_ttest_trad_test %>%
  left_join(baseline_preference_trad, by = "id") %>% 
  mutate(compare_value = case_when(target_word == "kem" ~ Mean - preference_kem,
                                   target_word == "bos" ~ Mean - preference_bos)) %>%
  group_by(familiarity, target_word) %>%
  do(broom::tidy(t.test(.$compare_value, mu = 0, data = .))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1)) 

#-------------------------------------------------Looking to kem and bos are significantly different from each other
data_ttest_trad_test %>%
  left_join(baseline_preference_trad, by = "id") %>% 
  mutate(compare_value = case_when(target_word == "kem" ~ Mean - preference_kem,
                                   target_word == "bos" ~ Mean - preference_bos)) %>%
  select(id, target_word, compare_value) %>%
  pivot_wider(names_from = "target_word", values_from = "compare_value") %>%
  do(broom::tidy(t.test(.$kem, .$bos, paired = TRUE, data = .))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1)) 

```

#### Group means
```{r ttests_corrected_means}

#-----------------------Dual lang means
data_ttest_trad_test %>%
  left_join(baseline_preference_trad, by = "id") %>% 
  mutate(compare_value = case_when(target_word == "kem" ~ Mean - preference_kem,
                                   target_word == "bos" ~ Mean - preference_bos)) %>% 
  filter(condition == "dual_lang") %>% 
  group_by(trad_analysis_group, familiarity, condition, experiment) %>%
  summarize(mean_compare_value = mean(compare_value),
            sd_compare_value = sd(compare_value),
            n = length(unique(id)))
  
#-----------------------Single lang means
data_ttest_trad_test %>%
  left_join(baseline_preference_trad, by = "id") %>% 
  mutate(compare_value = case_when(target_word == "kem" ~ Mean - preference_kem,
                                   target_word == "bos" ~ Mean - preference_bos)) %>% 
  filter(condition != "dual_lang") %>% 
  group_by(trad_analysis_group, familiarity, condition, experiment, target_word) %>%
  summarize(mean_compare_value = mean(compare_value),
            sd_compare_value = sd(compare_value),
            n = length(unique(id)))

#-----------------------Overall means

data_ttest_trad_test %>%
  left_join(baseline_preference_trad, by = "id") %>% 
  mutate(compare_value = case_when(target_word == "kem" ~ Mean - preference_kem,
                                   target_word == "bos" ~ Mean - preference_bos)) %>%
  summarize(mean = mean(compare_value),
            sd = sd(compare_value))

```

## Updated

### Check prename preference
```{r updated_prename_ttest}

#-----------------------Difference between looking to objects before utterances? Yes, slight kem preference
prename_data_updated_test %>%
  do(broom::tidy(t.test(.$prop ~ .$object, paired = TRUE, alternative = "two.sided"))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1))

#different way to get the same result:
prename_data_updated_test %>%
  filter(object == "kem") %>%
  do(broom::tidy(t.test(.$prop, mu = 0.5, data = .))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1)) 

#or linear model, since now with the bigger dataset might not make sense for paired t-test:
lm(prop ~ object, data = prename_data_updated_test) %>%
  summary(.)

prename_data_updated_test %>%
  group_by(object) %>%
  summarize(mean_prop = mean(prop),
            sd_prop = sd(prop))

```

### Uncorrected

#### Maximal models
```{r updated_maximal_models}

# intercept only - for later effect size calculation
lmer_null <- lme4::lmer(Prop - .5 ~ 1 + (1|target_word), 
                        data = data_lmer_updated_test_by_trial) #converges

#-------------------------------------------------Maximal: random slope (item) and intercept (id)
lmer_maximal_exposure <- lme4::lmer(Prop -.5 ~ per_exposure_target + (target_word|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

lmer_maximal_vocab <- lme4::lmer(Prop - .5 ~ vocab_target + (target_word|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

lmer_maximal_looking <- lme4::lmer(Prop - .5 ~ total_looking_time_training + (target_word|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

lmer_maximal_condition <- lme4::lmer(Prop - .5 ~ condition + (target_word|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

summary(lmer_null)

summary(lmer_maximal_exposure)
#ranef(lmer_maximal_exposure) 

summary(lmer_maximal_vocab)
#ranef(lmer_maximal_vocab) 

summary(lmer_maximal_looking)
#ranef(lmer_maximal_looking)

summary(lmer_maximal_condition)
#ranef(lmer_maximal_condition)

```

#### Pruned models
```{r updated_pruned_models}

#-------------------------------------------------Random intercepts: item and id 

lmer_rand_it_id_exposure <- lme4::lmer(Prop -.5 ~ per_exposure_target + (1|target_word) + (1|id), 
                          data = data_lmer_updated_test_by_trial) # singularity warning

lmer_rand_it_id_vocab <- lme4::lmer(Prop - .5 ~ vocab_target + (1|target_word) + (1|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

lmer_rand_it_id_looking <- lme4::lmer(Prop - .5 ~ total_looking_time_training + (1|target_word) + (1|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

lmer_rand_it_id_condition <- lme4::lmer(Prop - .5 ~ condition + (1|target_word) + (1|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

summary(lmer_rand_it_id_exposure)
#ranef(lmer_rand_it_id_exposure) 

summary(lmer_rand_it_id_vocab)
#ranef(lmer_rand_it_id_vocab) 

summary(lmer_rand_it_id_looking)
#ranef(lmer_rand_it_id_looking) 

summary(lmer_rand_it_id_condition)
#ranef(lmer_rand_it_id_condition) 


#-------------------------------------------------Random intercept: id only

lmer_rand_id_exposure <- lme4::lmer(Prop -.5 ~ per_exposure_target + (1|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

lmer_rand_id_vocab <- lme4::lmer(Prop - .5 ~ vocab_target + (1|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

lmer_rand_id_looking <- lme4::lmer(Prop - .5 ~ total_looking_time_training + (1|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

lmer_rand_id_condition <- lme4::lmer(Prop - .5 ~ condition + (1|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

summary(lmer_rand_id_exposure)
#ranef(lmer_rand_id_exposure)

summary(lmer_rand_id_vocab)
#ranef(lmer_rand_id_vocab) 

summary(lmer_rand_id_looking)
#ranef(lmer_rand_id_looking) 

summary(lmer_rand_id_condition)
#ranef(lmer_rand_id_condition) 


```

### Corrected for prenaming preference

#### Maximal models
```{r updated_maximal_models}

# intercept only - for later effect size calculation
lmer_null_cor <- lme4::lmer(difference_score ~ 1 + (1|target_word), 
                        data = data_lmer_updated_test_by_trial) #singular fit

#-------------------------------------------------Maximal: random slope (item) and intercept (id)
lmer_maximal_exposure_cor <- lme4::lmer(difference_score ~ per_exposure_target + (target_word|id), 
                        data = data_lmer_updated_test_by_trial) # converges

lmer_maximal_vocab_cor <- lme4::lmer(difference_score ~ vocab_target + (target_word|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

lmer_maximal_looking_cor <- lme4::lmer(difference_score ~ total_looking_time_training + (target_word|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

lmer_maximal_condition_cor <- lme4::lmer(difference_score ~ condition + (target_word|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

summary(lmer_maximal_exposure_cor)
#ranef(lmer_maximal_exposure_cor) 

summary(lmer_maximal_vocab_cor)
#ranef(lmer_maximal_vocab_cor) 

summary(lmer_maximal_looking_cor)
#ranef(lmer_maximal_looking_cor)

summary(lmer_maximal_condition_cor)
#ranef(lmer_maximal_condition_cor)

```

#### Pruned models
```{r updated_pruned_models_corrected}

#-------------------------------------------------Random intercepts: item and id 

lmer_rand_it_id_exposure_cor <- lme4::lmer(difference_score ~ per_exposure_target + (1|target_word) + (1|id), 
                          data = data_lmer_updated_test_by_trial) # singularity warning

lmer_rand_it_id_vocab_cor <- lme4::lmer(difference_score ~ vocab_target + (1|target_word) + (1|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

lmer_rand_it_id_looking_cor <- lme4::lmer(difference_score ~ total_looking_time_training + (1|target_word) + (1|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

lmer_rand_it_id_condition_cor <- lme4::lmer(difference_score ~ condition + (1|target_word) + (1|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

summary(lmer_rand_it_id_exposure_cor)
#ranef(lmer_rand_it_id_exposure_cor) 

summary(lmer_rand_it_id_vocab_cor)
#ranef(lmer_rand_it_id_vocab_cor) 

summary(lmer_rand_it_id_looking_cor)
#ranef(lmer_rand_it_id_looking_cor) 

summary(lmer_rand_it_id_condition_cor)
#ranef(lmer_rand_it_id_condition_cor) 

#-------------------------------------------------Random intercept: id only

lmer_rand_id_exposure_cor <- lme4::lmer(difference_score ~ per_exposure_target + (1|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

lmer_rand_id_vocab_cor <- lme4::lmer(difference_score ~ vocab_target + (1|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

lmer_rand_id_looking_cor <- lme4::lmer(difference_score ~ total_looking_time_training + (1|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

lmer_rand_id_condition_cor <- lme4::lmer(difference_score ~ condition + (1|id), 
                        data = data_lmer_updated_test_by_trial) # singularity warning

summary(lmer_rand_id_exposure_cor)
#ranef(lmer_rand_id_exposure_cor)

summary(lmer_rand_id_vocab_cor)
#ranef(lmer_rand_id_vocab_cor) 

summary(lmer_rand_id_looking_cor)
#ranef(lmer_rand_id_looking_cor) 

summary(lmer_rand_id_condition_cor)
#ranef(lmer_rand_id_condition_cor) 


```

### Final models

#### Uncorrected
````{r updated_pruned_models_final_uncorrected}

#-------------------------------------------------Random intercept: item only

lmer_rand_it_exposure <- lme4::lmer(Prop -.5 ~ per_exposure_target + (1|target_word), 
                        data = data_lmer_updated_test_by_trial) 

lmer_rand_it_vocab <- lme4::lmer(Prop - .5 ~ vocab_target + (1|target_word), 
                        data = data_lmer_updated_test_by_trial) 

lmer_rand_it_looking <- lme4::lmer(Prop - .5 ~ total_looking_time_training + (1|target_word), 
                        data = data_lmer_updated_test_by_trial) 

lmer_rand_it_condition <- lme4::lmer(Prop - .5 ~ condition + (1|target_word), 
                        data = data_lmer_updated_test_by_trial) 

summary(lmer_rand_it_exposure)
#ranef(lmer_rand_it_exposure)

summary(lmer_rand_it_vocab)
#ranef(lmer_rand_it_vocab) 

summary(lmer_rand_it_looking)
#ranef(lmer_rand_it_looking) 

summary(lmer_rand_it_condition)
#ranef(lmer_rand_it_condition) 

#---------------------------All predictors

lmer_rand_it_all <- lme4::lmer(Prop - .5 ~ per_exposure_target + vocab_target + total_looking_time_training + (1|target_word), 
                        data = data_lmer_updated_test_by_trial)

summary(lmer_rand_it_all)

#with target word as predictor

lmer_rand_id_all <- lme4::lmer(Prop - .5 ~ target_word + per_exposure_target + vocab_target + total_looking_time_training + (1|id), 
                        data = data_lmer_updated_test_by_trial) #Singular fit

#Simple linear model instead

lm_all <- lm(difference_score ~ target_word + per_exposure_target + vocab_target + total_looking_time_training, 
             data = data_lmer_updated_test_by_trial)
summary(lm_all)

#---------------------------separate models for each condition
lmer_exposure_two_lang <- 
  data_lmer_updated_test_by_trial %>% 
  filter(condition == "dual_lang") %>% 
  lme4::lmer(Prop - .5 ~ per_exposure_target + (1|target_word), 
                         data = .) # converge 

lmer_exposure_one_lang_foreign <- 
  data_lmer_updated_test_by_trial %>% 
  filter(condition == "single_lang_foreign") %>% 
  lme4::lmer(Prop - .5 ~ per_exposure_target + (1|target_word), 
                         data = .) # singular fit 

lmer_exposure_one_lang_native <- 
  data_lmer_updated_test_by_trial %>% 
  filter(condition == "single_lang_native") %>% 
  lme4::lmer(Prop - .5 ~ per_exposure_target + (1|target_word), 
                         data = .) # converge 


lmer_exposure_one_lang_all <- 
  data_lmer_updated_test_by_trial %>% 
  filter(str_detect(condition, "single_lang")) %>% 
  lme4::lmer(Prop - .5 ~ per_exposure_target + (1|target_word), 
                         data = .) # converge 

```

#### Corrected for prenaming preference

```{r updated_pruned_models_final_corrected}
#-------------------------------------------------Random intercept: item only

lmer_rand_it_exposure_cor <- lme4::lmer(difference_score ~ per_exposure_target + (1|target_word), 
                        data = data_lmer_updated_test_by_trial) #singular fit

lmer_rand_it_vocab_cor <- lme4::lmer(difference_score ~ vocab_target + (1|target_word), 
                        data = data_lmer_updated_test_by_trial) #singular fit

lmer_rand_it_looking_cor <- lme4::lmer(difference_score ~ total_looking_time_training + (1|target_word), 
                        data = data_lmer_updated_test_by_trial) #singular fit

lmer_rand_it_condition_cor <- lme4::lmer(difference_score ~ condition + (1|target_word), 
                        data = data_lmer_updated_test_by_trial) #singular fit

summary(lmer_rand_it_exposure_cor)
ranef(lmer_rand_it_exposure_cor)

summary(lmer_rand_it_vocab_cor)
ranef(lmer_rand_it_vocab_cor) 

summary(lmer_rand_it_looking_cor)
ranef(lmer_rand_it_looking_cor) 

summary(lmer_rand_it_condition_cor)
ranef(lmer_rand_it_condition_cor) 

#---------------------------All predictors

lmer_rand_it_all_cor <- lme4::lmer(difference_score ~ per_exposure_target + vocab_target + total_looking_time_training + (1|target_word), 
                        data = data_lmer_updated_test_by_trial) #singular fit

#---------------------------separate models for each condition
lmer_exposure_two_lang_cor <- 
  data_lmer_updated_test_by_trial %>% 
  filter(condition == "dual_lang") %>% 
  lme4::lmer(difference_score ~ per_exposure_target + (1|target_word), 
                         data = .) # singular fit 

lmer_exposure_one_lang_foreign_cor <- 
  data_lmer_updated_test_by_trial %>% 
  filter(condition == "single_lang_foreign") %>% 
  lme4::lmer(difference_score ~ per_exposure_target + (1|target_word), 
                         data = .) # singular fit 

lmer_exposure_one_lang_native_cor <- 
  data_lmer_updated_test_by_trial %>% 
  filter(condition == "single_lang_native") %>% 
  lme4::lmer(difference_score ~ per_exposure_target + (1|target_word), 
                         data = .) # singular fit  


lmer_exposure_one_lang_all_cor <- 
  data_lmer_updated_test_by_trial %>% 
  filter(str_detect(condition, "single_lang")) %>% 
  lme4::lmer(difference_score ~ per_exposure_target + (1|target_word), 
                         data = .) # singular fit  

#---------------------------Simple Linear Model

lm_target_word <-
  data_lmer_updated_test_by_trial %>%
  lm(difference_score ~ target_word + per_exposure_target + vocab_target + total_looking_time_training, data = .)

summary(lm_target_word)

```

### Model tables

#### Uncorrected
```{r model_tables_updated_uncorrected}

#intercept-only

tab_model(lmer_null,
          show.re.var = T,
          show.icc = T,
          title = "Intercept Only"#,
          #file = here("figures/table_lmer_exposure.doc")
          )

tab_model(lmer_rand_it_exposure,
          show.re.var = T,
          show.icc = T,
          title = "Exposure to target (%)"#,
          #file = here("figures/table_lmer_exposure.doc")
          )

tab_model(lmer_rand_it_vocab,
          show.re.var = T,
          show.icc = T,
          title = "Vocabulary in target language (n)"#,
          #file = here("figures/table_lmer_vocab.doc")
          )

tab_model(lmer_rand_it_looking,
          show.re.var = T,
          show.icc = T,
          title = "Total looking time during Training"#,
          #file = here("figures/table_lmer_training.doc")
          )

tab_model(lmer_rand_it_all,
          show.re.var = T,
          show.icc = T,
          title = "Word learning by multiple predictors"#,
          #file = here("figures/table_lmer_all_pred.doc")
          )


# joint table
tab_model(lmer_rand_it_exposure, lmer_rand_it_vocab, lmer_rand_it_looking, lmer_rand_it_all,
          show.re.var = T,
          show.icc = T,
          title = "Joint table: % exposure, vocabulary, looking time"#,
          #file = here("figures/table_lmer_exp_vocab_training.doc")
          )


tab_model(lmer_exposure_two_lang, lmer_exposure_one_lang_all,
          show.re.var = T,
          show.icc = T,
          title = "Exposure to target (%): 2-lang, 1-lang"#,
          #file = here("figures/table_lmer_exposur_by_conditione.doc")
          )

# simple model
tab_model(lm_target_word)

apaTables::apa.reg.table(lm_target_word,
                         #filename = here("figures/lm_table.rtf")
                         )

```

#### Corrected for prenaming preference

```{r model_tables_updated_corrected}


tab_model(lmer_rand_it_exposure_cor,
          show.re.var = T,
          show.icc = T,
          title = "Exposure to target (%)"#,
          #file = here("figures/table_lmer_exposure.doc")
          )

tab_model(lmer_rand_it_vocab_cor,
          show.re.var = T,
          show.icc = T,
          title = "Vocabulary in target language (n)"#,
          #file = here("figures/table_lmer_vocab.doc")
          )

tab_model(lmer_rand_it_looking_cor,
          show.re.var = T,
          show.icc = T,
          title = "Total looking time during Training"#,
          #file = here("figures/table_lmer_training.doc")
          )

tab_model(lmer_rand_it_all_cor,
          show.re.var = T,
          show.icc = T,
          title = "Word learning by multiple predictors"#,
          #file = here("figures/table_lmer_all_pred.doc")
          )


# joint table
tab_model(lmer_rand_it_exposure_cor, lmer_rand_it_vocab_cor, lmer_rand_it_looking_cor, lmer_rand_it_all_cor,
          show.re.var = T,
          show.icc = T,
          title = "Joint table: % exposure, vocabulary, looking time"#,
          #file = here("figures/table_lmer_exp_vocab_training.doc")
          )


tab_model(lmer_exposure_two_lang_cor, lmer_exposure_one_lang_all_cor,
          show.re.var = T,
          show.icc = T,
          title = "Exposure to target (%): 2-lang, 1-lang"#,
          #file = here("figures/table_lmer_exposur_by_conditione.doc")
          )

```

### Model assumptions


```{r updated_assumptions}
#------------------------------------Uncorrected
# DV distribution
hist(data_lmer_updated_test_by_trial$Prop - .5) # approximately normal

# residual distribution
plot(residuals(lmer_rand_it_exposure)) # random 

# Distribution of residuals
qqnorm(residuals(lmer_rand_it_exposure)) # approximately normal

## homogeneity of variance 
car::leveneTest(residuals(lmer_rand_it_exposure) ~ data_lmer_updated_test_by_trial$target_word) # is homogeneous
boxplot(residuals(lmer_rand_it_exposure) ~ data_lmer_updated_test_by_trial$target_word) # is homogeneous

#------------------------------------Corrected for prenaming preference

# DV distribution
hist(data_lmer_updated_test_by_trial$difference_score) # approximately normal

# residual distribution
plot(residuals(lmer_rand_it_exposure_cor)) # random 

# Distribution of residuals
qqnorm(residuals(lmer_rand_it_exposure_cor)) # approximately normal

## homogeneity of variance 
car::leveneTest(residuals(lmer_rand_it_exposure_cor) ~ data_lmer_updated_test_by_trial$target_word) # is homogeneous
boxplot(residuals(lmer_rand_it_exposure_cor) ~ data_lmer_updated_test_by_trial$target_word) # is homogeneous
```

# Visualizations

```{r palette}

#colourblind friendly palette

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#EFDC04", "#0072B2", "#D55E00", "#CC79A7")

```

## Traditional

### Dual language
```{r plot_trad_dual}

#---------------------------------------Plot with raw data, prename corrected

data_test_summarized_bilingual <- data_prop_by_word_trad_test %>%
  left_join(baseline_preference_trad) %>%
  mutate(Prop = case_when(target_word == "kem" ~ Prop - preference_kem,
                          target_word == "bos" ~ Prop - preference_bos),
         familiarity = snakecase::to_sentence_case(familiarity)) %>% 
  filter(condition == "dual_lang") %>%
  group_by(lang_group, familiarity, experiment) %>% 
  summarise(SD = sd(Prop), Prop = mean(Prop), n = length(unique(id))) %>% 
  mutate(SE = SD/sqrt(n),
         x_labels = snakecase::to_sentence_case(experiment)) 

#---------------------Get significance info from t-test section... right now this is done manually
sig_text <- tibble(x_labels = c("Experiment 1", "Experiment 4"), 
                   y = c(.175, .225),
                   familiarity = "Least familiar",
                   lab = c("**.009", "*.012"))

data_prop_by_word_trad_test %>%
  left_join(baseline_preference_trad) %>%
  mutate(Prop = case_when(target_word == "kem" ~ Prop - preference_kem,
                          target_word == "bos" ~ Prop - preference_bos),
         familiarity = snakecase::to_sentence_case(familiarity)) %>% 
  filter(condition == "dual_lang") %>%
  group_by(lang_group, familiarity, experiment) %>% 
  mutate(x_labels = snakecase::to_sentence_case(experiment))  %>%
  ggplot(aes(x = x_labels, y = Prop)) +
  geom_jitter(aes(color = x_labels, shape = x_labels), alpha = .33, stroke = 0, size = 2.25, width = .25) +
  geom_hline(yintercept = 0,linetype="dashed", color = "#010101", size = 1)+
  geom_errorbar(data = data_test_summarized_bilingual, aes(ymin = Prop - SE, ymax = Prop + SE), width=0.2,position=position_dodge(.9), color = "black") + 
  geom_point(data = data_test_summarized_bilingual, aes(color = x_labels, shape = x_labels), size = 3.5) +
  geom_label(data = data_test_summarized_bilingual, aes(label=paste("n =", n), y = -.675), color = "#010101", size = 5, label.size = 0, alpha = 0) +
  geom_text(data = sig_text, aes(y = y, label = lab), hjust = .5, size = 4) +
  facet_grid(. ~ fct_rev(familiarity), scales = "free", space = "free") +
  scale_color_manual(values = c(cbPalette[4], cbPalette[5], cbPalette[6], cbPalette[7])) +
  ylab("Proportion Looking to correct object\n(difference from baseline looking preference)") +
  xlab("Language Group") + 
  labs(color = "", shape = "") +
  ggtitle("Proportion looking to the correct object in the Test phase \ncompared to baseline looking preference (dual-language condition)") +
  scale_y_continuous(limits = c(-.75, .75), expand = c(0, 0)) +
  scale_shape_manual(values = c(15, 16, 17, 18)) +
  theme_bw(base_size=18)+ 
  theme(legend.position="right")+
  theme(axis.text.x = element_text(size=13), plot.title = element_text(hjust = 0.5))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) 

#ggsave(here("figures/dual_lang_condition_with_data_prename_corrected.png"), height = 6, width = 13)

```

### Single language
```{r plot_trad_dual}

#---------------------------------------Plot with raw data, prename corrected

data_test_summarized_mono <- data_prop_by_word_trad_test %>%
  left_join(baseline_preference_trad) %>%
  mutate(Prop = case_when(target_word == "kem" ~ Prop - preference_kem,
                          target_word == "bos" ~ Prop - preference_bos),
         familiarity = snakecase::to_sentence_case(familiarity)) %>% 
  filter(str_detect(condition, "single_lang")) %>%
  group_by(lang_group, familiarity, experiment) %>% 
  summarise(SD = sd(Prop), Prop = mean(Prop), n = length(unique(id))) %>% 
  mutate(SE = SD/sqrt(n),
         x_labels = snakecase::to_sentence_case(experiment)) 

data_prop_by_word_trad_test %>% 
  left_join(baseline_preference_trad) %>%
  filter(str_detect(condition, "single_lang")) %>%  
  mutate(Prop = case_when(target_word == "kem" ~ Prop - preference_kem,
                          target_word == "bos" ~ Prop - preference_bos),
         x_labels = snakecase::to_sentence_case(experiment),
         familiarity = snakecase::to_sentence_case(familiarity)) %>%
  ggplot(aes(x = x_labels, y = Prop)) +
  geom_jitter(aes(color = x_labels, shape = x_labels), alpha = .33, stroke = 0, size = 2.25, width = .25) +
  geom_hline(yintercept = 0,linetype="dashed", color = "#010101", size = 1)+
  geom_errorbar(data = data_test_summarized_mono, aes(ymin = Prop - SE, ymax = Prop + SE), width=0.2,position=position_dodge(.9), color = "black") + 
  geom_point(data = data_test_summarized_mono, aes(color = x_labels, shape = x_labels), size = 3.5) +
  geom_label(data = data_test_summarized_mono, aes(label=paste("n =", n), y = -.675), color = "#010101", size = 5, label.size = 0, alpha = 0) +
  facet_grid(. ~ fct_rev(familiarity), scales = "free", space = "free") +
  scale_color_manual(values = c(cbPalette[8], cbPalette[2], cbPalette[3])) +
  ylab("Proportion Looking to correct object") +
  xlab("Language Group") + 
  labs(color = "", shape = "") +
  ggtitle("Proportion looking to the correct object in the Test phase \ncompared to baseline looking preference (single-language condition)") +
  scale_y_continuous(limits = c(-.75, .75), expand = c(0, 0)) +
  scale_shape_manual(values = c(15, 16, 17))+
  theme_bw(base_size=18)+ 
  theme(legend.position="right")+
  theme(axis.text.x = element_text(size=13), plot.title = element_text(hjust = 0.5))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) 

#ggsave(here("figures/single_lang_condition_withd_data.png"), height = 6, width = 9)

```

## Updated

```{r visualizations_updated}
# Percentage of exposure to target (raw graph, 498 points)
plot_perc <- 
  data_lmer_updated_test_by_trial %>% 
  mutate(condition = case_when(str_detect(condition, "single_lang") ~ "Single language",
                          str_detect(condition, "dual_lang") ~ "Dual language")) %>%
  ggplot(aes(x = per_exposure_target, y = difference_score)) +
  geom_point(alpha = .15, color = cbPalette[7], shape = 16, stroke = 0, size = 2.25) +
  geom_smooth(method = "lm", alpha = .25, color = cbPalette[7], fill = cbPalette[7]) +
  ylim(c(-1, 1)) +
  labs(x = "Exposure to sentence frame languages (%)",
       y = "Proportion looking to correct object\nminus baseline looking preference") +
  #facet_wrap(~ condition) + # split by condition 
  theme_bw(base_size = 18) + 
  theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(hjust = 0.5),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())

#ggsave(here("figures/looking_raw_exposure_target_familiarity.png"), width = 12, height = 7, dpi = 300)

plot_perc

# Vocabulary (comprehension) (raw graph, 498 points)
plot_vocab <-  
  data_lmer_updated_test_by_trial %>% 
  mutate(condition = case_when(str_detect(condition, "single_lang") ~ "Single language",
                          str_detect(condition, "dual_lang") ~ "Dual language")) %>%
  ggplot(aes(x = vocab_target, y = difference_score)) +
  geom_point(alpha = 0.15, color = cbPalette[6], shape = 16, stroke = 0, size = 2.25) +
  geom_smooth(method = "lm", alpha = .25, color = cbPalette[6], fill = cbPalette[6]) +
  ylim(c(-1, 1)) +
  labs(x = "Vocabulary in sentence frame languages (n)",
       y = "Proportion looking to correct object\nminus baseline looking preference") +
  #facet_wrap(~ condition) + # split by condition
  theme_bw(base_size = 18) + 
  theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(hjust = 0.5),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())

#ggsave(here("figures/looking_raw_vocab_target.png"), width = 12, height = 7, dpi = 300)

plot_vocab

# Looking during Training (raw graph, 495 points)
plot_training <- 
  data_lmer_updated_test_by_trial %>% 
  mutate(condition = case_when(str_detect(condition, "single_lang") ~ "Single language",
                          str_detect(condition, "dual_lang") ~ "Dual language"))  %>%
  ggplot(aes(x = total_looking_time_training, y = difference_score)) +
  geom_point(alpha = 0.15, color = cbPalette[4], shape = 16, stroke = 0, size = 2.25) +
  geom_smooth(method = "lm", alpha = .25, color = cbPalette[4], fill = cbPalette[4]) +
  ylim(c(-1, 1)) +
  xlim(c(0, 50000)) +
  labs(x = "Total looking time during training (ms)",
       y = "Proportion looking to correct object\nminus baseline looking preference") +
  #facet_wrap(~ condition) + # split by condition
  theme_bw(base_size = 18) + 
  theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(hjust = 0.5),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())

#ggsave(here("figures/looking_raw_training_total_look.png"), width = 12, height = 7, dpi = 300)

plot_training

# Kem vs Bos

kembos_summary <- data_lmer_updated_test_by_trial %>%
  rename(mean = difference_score) %>%
  group_by(target_word) %>%
  summarize(difference_score = mean(mean, na.rm = TRUE), 
            sd = sd(mean, na.rm = TRUE),
            n = n()) %>%
  mutate(se = sd/sqrt(n),
         xmin = row_number() - .25,
         xmax = row_number() + .25)

plot_kembos <- 
  data_lmer_updated_test_by_trial %>% 
  ggplot(aes(x = target_word, y = difference_score)) +
  geom_jitter(aes(color = target_word), alpha = 0.2, shape = 16, stroke = 0, size = 2.25) +
  geom_errorbar(data = kembos_summary, aes(ymin = difference_score - se, ymax = difference_score + se), width = .2, color = "black") +
  stat_summary(aes(color = target_word), geom = "point", fun.y = "mean", shape = 16, stroke = 0, size = 2.25, alpha = 1) +
  ylim(c(-1, 1)) +
  labs(x = "Target word",
       y = "Proportion looking to correct object\nminus baseline looking preference") +
  scale_color_manual(values = c(cbPalette[8], cbPalette[5])) +
  scale_fill_manual(values = c(cbPalette[8], cbPalette[5])) +
  theme_bw(base_size = 18) + 
  theme(axis.text.x = element_text(size = 12),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(hjust = 0.5),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        legend.position = "none") 

#ggsave(here("figures/looking_by_target_word.png"), width = 12, height = 7, dpi = 300)

plot_kembos

# plot join
plot_join <- 
(plot_perc + theme(legend.position = "none") | plot_vocab + theme(axis.title.y = element_blank(), axis.text.y = element_blank())) / (plot_training | plot_kembos + theme(axis.title.y = element_blank(), axis.text.y = element_blank())) + plot_annotation(tag_levels = 'A')

plot_join

#ggsave(here("figures/plot_joint_colorized.png"), width = 14, height = 10, dpi = 300)



```

## Exclusions
```{r exclusion-plot}
library(ggalluvial)

trackloss_excl <- trackloss_trad_test %>% 
  distinct(id) %>% 
  filter(id %notin% response_window_trad_test$id) %>%
  mutate(excl_reason = "Not enough looking data")

missing_words <- response_window_trad_test %>% 
  distinct(id) %>% 
  filter(id %notin% data_trad_test$id) %>%
  mutate(excl_reason = "No data for both words")

excl_data <- participants %>%
  mutate(excl_reason = str_to_sentence(reason_exclusion),
         excl_reason = str_replace_all(excl_reason, "_", " "),
         excl_reason = str_replace(excl_reason, " age", " age of"),
         excl_reason = str_replace(excl_reason, "lang$", "language exposure"),
         excl_reason = str_replace(excl_reason, "quential", "quential bilingual"),
         excl_reason = str_replace(excl_reason, "Birth", "Low birth"),
         excl_reason = str_replace(excl_reason, "Language", "Language criteria not met"),
         excl_reason = str_replace(excl_reason, "Technical", "Technical issues"),
         excl_reason = str_replace(excl_reason, "Interference", "Parental interference")) %>%
  select(id = recording_name, excl_reason, keeper_new_analysis) %>%
  filter(id %notin% missing_words$id) %>%
  filter(id %notin% trackloss_excl$id) %>%
  full_join(trackloss_excl) %>%
  full_join(missing_words) %>%
  mutate(trad_sample = case_when(is.na(excl_reason) ~ 1),
         up_sample = case_when(trad_sample == 1 ~ 1,
                               id == "NovelDom14_S36_45223" ~ 0,
                               str_detect(excl_reason, "criteria") ~ 1,
                               str_detect(excl_reason, "No data") ~ 1),
         recruited = "Recruited and Tested")

excl_data_plot <- excl_data %>%
  count(recruited, excl_reason, trad_sample, up_sample)

# ggplot(data = excl_data_plot,
#        aes(axis1 = recruited, axis2 = excl_reason, axis3 = trad_sample, axis4 = up_sample, y = n)) +
#   geom_alluvium(aes(fill = up_sample)) +
#   geom_stratum() +
#   geom_text(stat = "stratum",
#             aes(label = after_stat(stratum))) +
#   scale_x_discrete(limits = c("Survey", "Response"),
#                    expand = c(0.15, 0.05)) +
#   theme_void()


```

# Looking while listening versus Switch task

This analysis compares the effect size found in our experiment with the Looking while listening paradigm, with the effect sizes of 14-month-old infants learning dissimilar sounding words in a Switch task. 

Data for the Switch task comes from a meta-analysis by Tsui, Byers-Heinlein, and Fennell (2019) and is openly available at:

OSF: https://osf.io/uwe8g/ 
MetaLab: http://metalab.stanford.edu/dataset/switchtask/ 

Tsui, A. S. M., Byers-Heinlein, K., & Fennell, C. T. (2019). Associative word learning in infancy: A meta-analysis of the switch task. *Developmental Psychology, 55*(5), 934950. https://doi.org/10.1037/dev0000699

## Effect size and power analysis

Looking while listening - Effect size

Overall traditional *Cohen's d*, with 1 observation (average) per participant and assuming independence.
  
```{r}
# aggregate data by participant (1 proportion per participant)
agg_id_d <- 
  data_lmer_updated_test_by_trial %>% 
  group_by(id) %>% 
  summarise(mean_prop = mean(Prop, na.rm = T),
            chance_level = 0.5)

# calculate Cohen's d
d_stats <- 
  agg_id_d %>%
  summarise(mean = mean(mean_prop, na.rm = T),
            sd = sd(mean_prop, na.rm = T),
            chance_level = 0.5,
            d = (mean - chance_level)/sd,
            n = n_distinct(data_lmer_updated_test_by_trial$id), #HK updated this
            alpha = 0.05,
            z_crit = qnorm(1-alpha/2),
            se = sqrt(1/n + d^2/(2*n)),
            d_lower = d-se*z_crit,
            d_upper = d+se*z_crit
            )
```

## Approximate effect size for mixed models: $\omega^2$

```{r}
# calculate omega squared as an approximate effect size for mixed models
omga_perc_exposure = effectsize::omega_squared(lmer_rand_it_exposure, ci = 0.95)
omga_vocab = effectsize::omega_squared(lmer_rand_it_vocab, ci = 0.95)
omga_training = effectsize::omega_squared(lmer_rand_it_looking, ci = 0.95)

omga_perc_exposure
omga_vocab
omga_training
```

## Approximate effect size from Brysbaert & Stevens (2018) - http://doi.org/10.5334/joc.10 
$$
\begin{array}{l}
d = \,\,\frac{{difference\, between\, the\, means}}{{\sqrt {varintercep{t_{part}} + varintercep{t_{item}} + varslop{e_{part}} + varslop{e_{item}} + va{r_{residual}}}}}\\
\end{array}
$$

```{r}
# from null model
summary(lmer_null)

# mixed d
mixed_d <- 0.02252 / sqrt(0.002901 + 0.063872)
round(mixed_d, 2)
```

## Observed effect size based on simulation

We will simulate and approximate the effect size for a single predictor at a time.
These are simulation-based power analysis, it may take some time to run them. By default, they are turned off. Turn them on using the switch in the code below. 

```{r}
# switch
run_simr <- F 

if(run_simr == T){
# number of simulations
nsim = 500

# predictors: 
pwr_sim_lmer_rand_it_exposure <- simr::powerSim(lmer_rand_it_exposure, # per_exposure_target
                                     nsim = nsim) 

pwr_sim_lmer_rand_it_vocab <- simr::powerSim(lmer_rand_it_vocab, # vocab_size
                                     nsim = nsim) 

pwr_sim_lmer_rand_it_looking <- simr::powerSim(lmer_rand_it_looking, # looking during training
                                     nsim = nsim) 

# effect sizes
pwr_sim_lmer_rand_it_exposure # 0.000004
pwr_sim_lmer_rand_it_vocab # 0.00011
pwr_sim_lmer_rand_it_looking # -0.0000001

}
```

##  Switch task - Effect size

Here we use open data from:
Tsui, A. S. M., Byers-Heinlein, K., & Fennell, C. T. (2019). Associative word learning in infancy: A meta-analysis of the switch task. Developmental Psychology, 55(5), 934950. https://doi.org/10.1037/dev0000699

## Load dataset

```{r}
switch_ma <- read.csv(here("data/Switch task.csv"))
```

## Filter dataset

- Age: Same age range as our research, "13 months and 16 days  15 months and 12 days"
- Word type: "dissimilar sounding"

```{r}
# month to days (metalab convention = 30.44)
min_age <- 13*30.44 + 16
max_age <- 15*30.44 + 12

# filter
switch_ma_filtered <- 
  switch_ma %>% 
  filter(minimal_pairs == "dissimilar sounding",
         mean_age >= min_age,
         mean_age <= max_age)
```

## Descriptive stats

- Number of studies;
- Number of participants;
- Mean age, sex etc.

```{r}
switch_ma_filtered %>% 
  summarise(studies_n = nrow(.),
            total_n = sum(n, na.rm = T),
            prop_female = mean(gender_1, na.rm = T), 
            mean_age_days = mean(mean_age, na.rm = T), 
            mean_age_months = mean_age_days/30.44)
```

## Estimate effect-size

- Use the `metafor` package to run a mini-MA
- Double check code with Metalab code (will I be able to decypher it??)

```{r}
switch_mini_ma <- metafor::rma(d, d_var, data = switch_ma_filtered)
summary(switch_mini_ma)

# estimate effect size
switch_mini_ma$b

# forest plot
metafor::forest(switch_mini_ma)
```

# Power analysis

Here we estimate the sample size necessary to detect word learning significantly above chance using the effect size of the Switch Task. 
We start calculating Power for the t-tests, then we estimate power for mixed-models.

## Traditional analysis: t-test

```{r}
# power, t-test, one-sample against chance
pwr::pwr.t.test(d = 0.33, # ES switch task
                sig.level = 0.05, # alpha
                power = 0.80, # 1-beta
                type = "one.sample",
                alternative="two.sided")

## required sample size = 75 participants
```

## Updated analysis: mixed-models

These are simulation-based power analysis, it may take some time to run them. By default, they are turned off. Turn them on using the switch in the code below. 
One predictor at a time.

```{r}
# trun switch on and off on step 8.1.4.
if(run_simr == T){
  
# power curve for mixed-models
pc_lmer_rand_it_exposure <- powerCurve(lmer_rand_it_exposure)
pc_lmer_rand_it_vocab <- powerCurve(lmer_rand_it_vocab)
pc_lmer_rand_it_looking <- powerCurve(lmer_rand_it_looking)

# power and 95% CI
print(pc_lmer_rand_it_exposure)
print(pc_lmer_rand_it_vocab)
print(pc_lmer_rand_it_looking)

# power curve
plot(pc_lmer_rand_it_exposure)
plot(pc_lmer_rand_it_vocab)
plot(pc_lmer_rand_it_looking)

}
```

